---
title: "CLT_WUP"
author: "David Barton"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.


```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg


p <- ggplot(my1000, aes(x=k9),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```


For the sample size of nine. based on the Central limit theorem, the graph shows that mean gets closer to 50 when it is rounded up, and standard deviation is decreasing. Due to the clt theorem it is expected to decrease with the sample standard deviation was 41.6342455365941 and when the sample sizes increase, here 9 and when divded the sample standard deviation by sqaure root of 9 it will add up to be 14.0066225. That is close to the results I got which rounds up or down the fourteen. It shows that the graph is getting more and more symmetrical.

```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg


p <- ggplot(my1000, aes(x=k16),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

For the sample size of 16. based on the Central limit theorem, the graph shows that mean gets closer to 50 when it is rounded up, and standard deviation is decreasing. Due to the clt theorem it is expected to decrease with the sample standard deviation was 41.6342455365941 and when the sample sizes increase, here 9 and when divded the sample standard deviation by sqaure root of 9 it will add up to be 10.5. That is close to the results I got which rounds up or down the fourteen. It shows that the graph is getting more and more symmetrical.




```{r}
numb = 25
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg


p <- ggplot(my1000, aes(x=k25),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k25)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```


For the sample size of 25. based on the Central limit theorem, the graph shows that mean gets closer to 50 when it is rounded up, and standard deviation is decreasing. Due to the clt theorem it is expected to decrease with the sample standard deviation was 41.6342455365941 and when the sample sizes increase, here 25 and when divided the sample standard deviation by sqaure root of 9 it will add up to be 8.4. That is close to the results I got which rounds up or down the fourteen. It shows that the graph is getting more and more symmetrical.



```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg


p <- ggplot(my1000, aes(x=k36),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

For the sample size of 36. based on the Central limit theorem, the graph shows that mean gets closer to 50 when it is rounded up, and standard deviation is decreasing. Due to the clt theorem it is expected to decrease with the sample standard deviation was 41.6342455365941 and when the sample sizes increase, here 36 and when divided the sample standard deviation by sqaure root of 36 it will add up to be 7.00331126. That is close to the results I got which rounds up or down the 7.0. It shows that the graph is symmetrical.

